### 2014-02-13 tex/pseudo-code.tex
Added some stuff

\section{Pseudo-code}
The presentation assumes a CEKS machine for a Java-like language
(mostly a syntactic machine) \cite{saints-MS}. The machine state for
the semantics consists of a (C)ontrol string representing the
expression being evaluated, an (E)nvironment for local variables, a
(K)ontinuation for what is to be executed next, and a (S)tore for the
heap. This paper only defines salient features of the machine relevant
to understanding the new algorithm.

The language is defined as in the following figure.
\input{grammar}

>>>>

\section{Pseudo-code}
\figref{fig:surface-syntax} defines the surface syntax for the
Javalite language \cite{saints-MS}. The \figref{fig:machine-syntax} is
the machine syntax. The semantics of Javalite is syntax based and
defined as rewrites on a string. The semantics use a CEKS machine
model with a (C)ontrol string representing the expression being
evaluated, an (E)nvironment for local variables, a (K)ontinuation for
what is to be executed next, and a (S)tore for the heap. This paper
only defines salient features of the language and machine relevant to
understanding the new algorithm.

\input{surface-syntax}
\input{machine-syntax}
